Javelins with hyper3 objects

### 2022-04-18 inst/javelin.Rmd
clarification

```{r,label=loadjavelinandconvert}
javelin_table <- read.table("javelin.txt",header=TRUE)
a <- javelin_table # saves typing

o <- attemptstable2supp3(a,decreasing=TRUE,give.supp=FALSE)
```

Plot the data in visual form:

@@

Now process it:

```{r,label=dothething1,cache=TRUE}    	   
javelin <- attemptstable2supp3(a,decreasing=TRUE,give.supp=TRUE)
H1 <- javelin # saves typing
javelin1_maxp <- maxp(H1)
m1 <- javelin1_maxp
```

```{r,label=dothething2,cache=TRUE}    	   
H2 <- ordervec2supp3(v=names(o)[!is.na(o)])
javelin2_maxp  <- maxp(H2)
m2 <- javelin2_maxp
```

```{r,plotm}
pie(m1)
pie(m2)
dotchart(m1,pch=16)
dotchart(m2,pch=16)
par(pty="s")
plot(m1,m2,pch=16,type="p",asp=1)
abline(0,1)
```

>>>>

```{r,label=loadjavelinandconvert}
javelin_table <- read.table("javelin.txt",header=TRUE)
a <- javelin_table # saves typing
javelin_table
```

Above, we see that Chopra threw 87.03m on his first throw, 87.58m on
his second, and so on.  Vadlejch threw 83.98m on his first throw, etc.
We may convert this to a named vector with elements being the throw
distances, and names being the competitors, using
`attemptstable2supp3()`:

```{r,label=converttosupp3,cache=TRUE}
javelin_vector <- attemptstable2supp3(a,decreasing=TRUE,give.supp=FALSE)
javelin_vector
o <- javelin_vector # saves typing
```

Above we see that Chopra threw the longest and second-longest throws
of 87.58m and 87.03 respectively; Vadlejch threw the third-longest
throw of 86.67m, and so on.  It is easy to plot the data in visual
form:

@@

Now convert the attempts table to a `hyper3` object, again using
function `attemptstable2supp3()` but this time pass `give.supp=TRUE`.
However, note that there are two reasonable interpretations: firstly,
we simply ignore no-throws [in the package docs, these are sometimes
referred to as "DNF", or "Did not finish", following Formula 1
terminology]:

```{r,label=dothething2,cache=TRUE}    	   
javelin1 <- ordervec2supp3(v=names(o)[!is.na(o)])
H1 <- javelin1 # saves typing
javelin1_maxp  <- maxp(H1)
m1 <- javelin1_maxp
```

Secondly, we may treat no-throws as being inferior to any actual
measured throw.  To do this it is easiest to pass `give.supp=TRUE` to
`attemptstable2supp3()`:

```{r,label=dothething1,cache=TRUE}    	   
javelin2 <- attemptstable2supp3(a,decreasing=TRUE,give.supp=TRUE)
H2 <- javelin2 # saves typing
javelin2_maxp <- maxp(H2)
m2 <- javelin2_maxp
```

Inveestigation:

```{r,plotm}
rbind(one=m1,two=m2)
pie(m1)
pie(m2)
dotchart(m1,pch=16)
dotchart(m2,pch=16)
par(pty="s")
plot(m1,m2,pch=16,type="p",asp=1)
abline(0,1)
```
